\begin{appendices}
    \section{Contribution of Members}
    \subsection{Tuna Alikaşifoğlu}
    Tuna was responsible for several aspects of the project. First, he was responsible for data pre-processing with (Distil-) BERT tokenization techniques to convert the documents to list of input IDs, which corresponds to the text representations that are both used in generation of BERT and GNN embeddings. He was also responsible for generation of (Distil-) BERT embeddings to be used in the aggregation step. Finally, he implemented an efficient way to generate graph adjacency matrix \(\mat{A}\) with sparse representation.

    \subsection{Arda Can Aras}
    Arda was responsible for researching and understanding the novel GNN algorithms and their implementations in text classification. He has implemented Graph Neural Network architecture, with different setups and proposed a learnable adjacency matrix \mat{A} as a novelty. He also implemented the three different aggregation layer strategies and classification layer. Arda was also responsible of fine-tuning the Distil-BERT on 20NG dataset.
    \clearpage

    \onecolumn
    \section{Source Code}
    \begin{pycode}
from pathlib import Path
report_path = Path.cwd()
work_dir_path = report_path.parent
python_files = list(work_dir_path.rglob('*.py'))
python_files.pop(-1)
python_files = python_files[::-1]
for f in python_files:
    title = f.name.replace("_", "\\_")
    print(r"\subsection{" + f"{title}" + r"}")
    print(r"\inputminted[linenos,fontsize=\scriptsize]{python}{" + f"{f}" + r"}")
\end{pycode}

\end{appendices}

