\section{Introduction}
In this survey, we have scrutinize the classic natural language processing task of text classification along with the trending approach of graph neural networks. We have divided the survey into two parts: \emph{Previous Work} (\cref{sec:previous}) and \emph{Related Work} (\cref{sec:related}). In~\cref{sec:previous}, we provide an overview regarding the traditional text classification (\cref{sec:TC}) and we provide an overview to graph neural networks (\cref{sec:GNN}). Both of these overviews are provided based on several survey papers for text classification~\autocite{kowsari19tc,li20tc,minaee20tc} and for graph neural networks~\autocite{zhou20gnn,wu21gnn,zhang18dlongraphs,sun18adversarial}. In~\cref{sec:TC}, we provide a basic definition for text classification, then we disintegrate text classification process to five steps to analyse the overall process, and we point out where the integration of graph neural networks can be made. In~\cref{sec:GNN}, we provide an introduction to graph neural networks. Then, we analyse why we need graph neural networks, we provide several challenges on the route of obtaining graph based deep learning frameworks, and finally we provide bare-minimum steps in order to obtain a graph neural network based architecture, based on the aforementioned surveys, in this subsection. After this step, we are at a stage that we have provided background information both on the preliminary aspects of the overall term project, which are text classification and graph neural networks. 

In~\cref{sec:related}, we provide previous work directly related to our own topic of graph neural networks related to solution of the classical natural language processing task of text classification. \cref{sec:related} of the survey aims to investigate the related and previous work in the text classification with graph neural network field possibly with a historical order. All the papers mentioned in this section related with each other by references. Surprisingly, this structure can also be viewed as graph where each paper is node and and edges of the graphs as citation. There are also studies on this topic to predict structured citation trend~\autocite{citationGNN}. Most of the papers in the~\cref{sec:related} did not directly proposed to solve text classification task. However, nearly all of the papers presented~\cref{sec:related} used text classification bench mark data sets to evaluate model performance.
