\documentclass[a4paper, 12pt, conference]{IEEEtran}
\usepackage[utf8]{inputenc}
\usepackage[style=ieee]{biblatex}
\usepackage{amsmath}
\usepackage{hyperref}
\usepackage[capitalise,nameinlink]{cleveref}
\usepackage{lipsum}

\title{EEE 586: Survey for the Term Project\\Text Classification with Graph Neural Networks}
\author{
    \IEEEauthorblockN{Tuna Alikaşifoğlu}
    \IEEEauthorblockA{\textit{Dept.\ of Electrical and Electronics Engineering} \\ \textit{Bilkent University}\\\href{mailto:t.alikasifoglu@bilkent.edu.tr}{\texttt{t.alikasifoglu@bilkent.edu.tr}}}
    \and
    \IEEEauthorblockN{Arda Can Aras}
    \IEEEauthorblockA{\textit{Dept.\ of Electrical and Electronics Engineering} \\ \textit{Bilkent University}\\\href{mailto:can.aras@bilkent.edu.tr}{\texttt{can.aras@bilkent.edu.tr}}}
}
\date{\today}
\bibliography{bibliography}
\hypersetup{
    colorlinks=true,
    linkcolor=[rgb]{0.6,0,0},
    citecolor=[rgb]{0,0.6,0},
    urlcolor=[rgb]{0,0,0.6},
    % allcolors=black
    pdftitle={EEE 586 Survey-Group 16},
    bookmarksopen=true,
}
\allowdisplaybreaks{}

\begin{document}
\maketitle
\thispagestyle{plain}
\pagestyle{plain}
\IEEEtitleabstractindextext{
    \begin{abstract}
        In recent years, the amount of text based complex documents increased significantly, along with the importance of ability to classify texts as efficiently and accurately as possible. We had traditional algorithms to tackle the text classification problem, but with the progressive computational power, many machine learning, especially deep learning, based solutions surpassed the human capabilities in this area. On the other hand, we have the trending topic of graph neural networks. They are geometric extensions, i.e., extensions of traditional neural network architectures to the graph domain, and graph-structured data. In this survey, a brief overview of text classification problem and of graph neural networks are provided. Text classification overview covers the fundamental steps of a text classification task with the indication of graph neural network integration, where the graph neural network overview provides the reasons, challenges and how-tos of utilizing graph neural networks. Finally, we provide an overview of the related work that tackles the text classification problem with the graph neural networks, while comparing several approaches.
    \end{abstract}
    \begin{IEEEkeywords}
        Text Classification, Graph Neural Networks (GNNs), Graph Convolutional Networks (GCNs), Convolutional Graph Neural Networks (ConvGNNs).
    \end{IEEEkeywords}
}
\IEEEdisplaynontitleabstractindextext{}

\input{intro}
\input{previous}
\input{related}

\newpage
\printbibliography{}
\end{document}